---
title: "TITLE"
subtitle: "SUBTILE"
author: 
  - name: "Lars Schöbitz"
    url: https://www.lse.de
    affiliation: Global Health Engineering, ETH Zurich
    affiliation_url: https://ghe.ethz.ch/
    orcid_id: 0000-0003-2196-5015 
  - name: "Prof. Dr. Elizabeth Tilley"
    url: https://ghe.ethz.ch/about/people/person-detail.MTc2MjI5.TGlzdC80MTI2LC0xNDYwMDMwNTU3.html
    affiliation: Global Health Engineering, ETH Zurich
    affiliation_url: https://ghe.ethz.ch/
    orcid_id: 0000-0002-2095-9724
format: 
  docx:
    number-sections: true
    toc: true
  gfm:
    number-sections: true
citation: true
bibliography: references.bib
csl: vancouver-brackets-no-et-al.csl
---

```{r}
#| label: setup
library(epoxy)
library(tidyverse)
```

```{r}
#| label: load-data

tbl04 <- read_csv(here::here("data/tbl-04-wp-activities.csv"))

wp_no <- tbl04$wp

wp_name <- tbl04$name 

```

```{r}

```
# Call Info

## Website

- Measure 1: Calls for Field-Specific Actions
- https://ethrat.ch/en/measure-1-calls-for-field-specific-actions/
- Contribute projects will help researchers to contribute to existing open communities built around ORD. They will validate their integration with existing infrastructures (including international ones) and focus on their potential to advance the scientific impact of the field as well as their technical quality.

## Aims

Funding for “Contribute projects” aims at:

- Contributing a piece of software, data, hardware, etc., which simplifies an established ORD practice, develops its research potential, or otherwise improves it.

- Curating or otherwise improving available ORD, for example, by updating existing data to adapt it to the evolution of ORD practices or by linking different ORD datasets or by collecting and curating existing data before uploading it to an ORD platform.

- Providing community services, such as the organization of a workshop or training, or coordination for the development of an ORD standard.

## Application guidelines

- https://ethrat.ch/wp-content/uploads/2023/10/Application-guidelines_TrackC-Contribute-projects-6th-call-FINAL.pdf
- Preference will be given to projects which engage and are connected to a community

## Application guidelines (ETH Zurich)

- https://ethrat.ch/wp-content/uploads/2022/06/2022-05-00-ETH-ORD-EPFLETHZ-information-to-applicants-Contribute.pdf
- For applicants at ETHZ
- In this Contribute call, applicants at ETHZ must contribute 25% of the total budget from the resources of their lab/group/unit, either in-cash or  in-kind. See the budgeting guidelines below for eligible contributions
- This means an additional 22’500 CHF for us and 7’500 CHF in-kind through my salary

# Project Proposal

Your project proposal must not exceed 6 pages, excluding the bibliography (A4, Arial 11-point font, 1.5 line-spacing, 2-centimeter margins). Please address all points below.

# Abstract

TODO: Get instructions from submission portal

# Proposal full title

**Instructions**

Please include a project title (max. 12 words); this title will be used for all correspondence. Proposal Acronym (mandatory)

# Background and motivation

**Instructions**

Please explain which aim(s) of the ORD “contribute projects” you seek to address:

- Contributing a piece of software, data, hardware, etc., which simplifies an established ORD practice, develops its research potential, or otherwise improves it.

- Curating or otherwise improving available ORD. For example, by updating existing data to adapt it to the evolution of ORD practices. Or by linking different ORD datasets. Or by collecting and curating existing data before uploading it to an ORD platform.

- Providing community services, such as the organization of a workshop or training, or coordination for the development of an ORD standard.


## WASH Web

-   One paragraph. 50 to 70 words

## openwashdata

-   One paragraph. 50 to 70 words

## Common goals

-   One to two paragraphs (100 to 150 words)

## Problem statement

-   One to two paragraphs (100 to 150 words)

# ORD project plan

**Instructions**

Please describe your project design, including how it addresses the aim(s) of the ORD “contribute projects” described above. Please refer to the scientific literature as well as any preliminary, unpublished results that have informed your approach.

- Which specific gap(s) in knowledge will your work address? Why is your approach innovative?
- What questions will the project answer? What specific outcomes will you focus on?
- Which strategy will you use to address the questions you seek to answer?

## `r paste0(wp_no[1], ": ", wp_name[1])`

**Goal**:

-   Describe the work concisely in 1 paragraph (80 to 120 words)

**Activities**

1.  A
2.  B
3.  C

**Aims addressed**

-   This is related to the aims of the Contribute call and we need to describe specifically how they are addressed by this WP

## `r paste0(wp_no[1], ": ", wp_name[1])`

**Goal**:

-   Describe the work concisely in 1 paragraph (80 to 120 words)

**Activities**

1.  A
2.  B
3.  C

**Aims addressed**

-   This is related to the aims of the Contribute call and we need to describe specifically how they are addressed by this WP

## `r paste0(wp_no[1], ": ", wp_name[1])`

**Goal**:

-   Describe the work concisely in 1 paragraph (80 to 120 words)

**Activities**

1.  A
2.  B
3.  C

**Aims addressed**

-   This is related to the aims of the Contribute call and we need to describe specifically how they are addressed by this WP

## `r paste0(wp_no[1], ": ", wp_name[1])`

**Goal**:

-   Describe the work concisely in 1 paragraph (80 to 120 words)

**Activities**

1.  A
2.  B
3.  C

**Aims addressed**

-   This is related to the aims of the Contribute call and we need to describe specifically how they are addressed by this WP

# Impact

Please address these specific points: 

- How sustainable is the proposed project inside the ETH Domain? 
- To what extent may an existing or a newly formed community (be able to) engage with the ORD practice(s) built-up during the project?

# Work Packages and milestones

The following Table 2 shows a basic gantt chart against the four work packages, including program activities and community engagement. Column “Lead” abbreviations: 

Any publications derived from this program will be published as open access material, following ORD practices and Open Science standards for computational reproducibility and sharing of data and code under FAIR principles.   

Table 2: https://docs.google.com/spreadsheets/d/1xMlMepWoq4lTRRP89x8A1A-1Bkqkn7hjslvpJ5XPXU8/edit#gid=0

# Resources (including project costs)

Table 4: https://docs.google.com/spreadsheets/d/1OKAFWg4PyPp7_BikkQOh9QQ8t982iOTHsB1c5A6SoqU/edit#gid=0

# Bibliography